A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-30 writeup/paper.tex
Added question

We performed an analysis of our data to address the following questions, among others:
\begin{itemize}
\item How quickly can we expect work to be completed in a particular language? 
\item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
\item How prevalent is the use of machine translation? 
%\item What is the quality of crowdsourced translations without quality control versus with it? 
\end{itemize}

>>>>

We performed an analysis of our data to address the following questions:
\begin{itemize}
\item How quickly can we expect work to be completed in a particular language? 
\item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
\item Is the use of machine translation prevalent?  
\item Are our gold standard translations valid? 
%\item What is the quality of crowdsourced translations without quality control versus with it? 
\end{itemize}
